A quantitative framework for investigating the reliability of empirical network construction

### 2019-03-14 manuscript/CI_interactions.tex
added a dumb repo for redundant code access

Data from~\citet{Kopelke2017} used in this manuscript is available from \emph{https://doi.org/10.1002/ecy.1832}. Data from~\citet{Barbour2016} used in this manuscript is available from \emph{https://doi.org/10.5061/dryad.g7805}. All code used in this manuscript is available in the online supporting information.

>>>>

Data from~\citet{Kopelke2017} used in this manuscript is available from \emph{https://doi.org/10.1002/ecy.1832}. Data from~\citet{Barbour2016} used in this manuscript is available from \emph{https://doi.org/10.5061/dryad.g7805}. All code used in this manuscript is available in the online supporting information or can be accessed via \emph{github.com/cirtwill/Constructing-quantitative-interaction-networks} or https://doi.org/10.5281/zenodo.2593695.
